Fit by design: Developing substrate-specific seed mixtures for functional dike grasslands

### 2023-03-09 manuscript.Rmd
Update manuscript.Rmd

Characteristics of the substrates used for the sowing experiment on river dikes. Soil samples of the three substrates were analysed for the fraction \<2 mm. The soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005]. The pH was measured in CaCl~2~ solution. Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in a CaCl~2~ extract. For calculating CaCO~3~, a sub-sample was annealed at 550 °C and the measured C amount multiplied with 8.33. To calculate total N and the C/N ratio, a sub-sample was incinerated at 1000 °C. Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand.<!--# Humusanteil-->

@@

```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_2_nmds_800dpi_16.5x16cm.tiff")
  )
```

@@

```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_3_800dpi_16.5x5cm.tiff")
  )
```

@@

```{r fig.id = "interactions", fig.asp = 1.2121, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_4_800dpi_16.5x20cm.tiff")
  )
```

>>>>

Characteristics of the substrates used for the sowing experiment on river dikes. Soil samples of the three substrates were analysed for the fraction \<2 mm. The soil texture was classified according to the 'Bodenkundliche Kartieranleitung' [@BodenkundlKartieranl.2005]. The pH was measured in CaCl~2~ solution. Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in a CaCl~2~ extract. For calculating CaCO~3~, a sub-sample was annealed at 550 °C and the measured C amount multiplied with 8.33. To calculate total N and the C/N ratio, a sub-sample was incinerated at 1000 °C. Lt3 = medium clayey loam; Ls4 = strong sandy loam; Sl3 = medium loamy sand; Sl4 = strong loamy sand.

@@

```{r fig.id = "nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_2_nmds_600dpi_16.5x16cm.tiff")
  )
```

@@

```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_3_600dpi_16.5x5cm.tiff")
  )
```

@@

```{r fig.id = "interactions", fig.asp = 1.2121, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_4_600dpi_16.5x20cm.tiff")
  )
```
